---
title: "linear model from Web"
author: "Juan Moreno"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS


### scatterplot
```{r}
SAP <- ggplot(data,aes(y=SIMS,x=ARM))
SAP + geom_point()
```

Looking at the scatter plot i can see that there is a linear relationship between the Simulation and Arms

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
The coefficient is close to one meaning that the simulation isn't far off with its data but still not a completely strong enough data.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
the slope is 0.5 and its explaining 46% of the data that wasn't explained by earlier data tables.


#### Predict at target point

```{r}
TP <- data.frame(ARM=88, GRIP=94)
predict(model.1, TP, interval ="prediction")
```
This is the process of using a code to predict the targets   point for arm when its 94% value or 94% confident where   the target point where lie.  

#### scatterplot with model fit
```{r}
SAP + geom_point() + geom_lm()
```

The line seen in the scatter plot is the prediction line   which is taking the target point from above and adding it   to the scatter plot from earlier.  

## Model 2 SIM~GRIP



### Now add in scatterplot

```{r}
SGP <- ggplot(data,aes(y=SIMS,x=ARM))
SGP + geom_point()
```

Here we have a visual about the data. which aligns with the findings from the case study. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
Almost the same as before, the numerical result came close to 0 which means we are still not to far off with the data but still could use more data analysis.  

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

In the data sheet above we can see more detailed   information inn relation of the Simulation and Grip and   once again explaining 40% of the data.  


#### predict model.2 at target point

```{r}
predict(model.2, TP, interval ="prediction")
```
We can now see the prediction model for the simulation and grip of what would make a good candidate to be hired for   the job.  

#### now add the model fit to our plot for model.2
  
  
```{r}
SGP + geom_point() + geom_lm()
```

Taking the prediction data from above we can added to our   graph and see that there is a slight linear relation ship   with the scatter plot but it is not one that cant be seen   right in the beginning.  


## Model 3 SIM~ARM+GRIP


### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

No longer looking into just one variable we are now   looking at two variables at the same time, notice how the   numerical results of both arm and grip is higher then if   we were to look at one on its own. surely conforming out   theory.  

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

#### predict model.3 at target point
  
```{r}
predict(model.3, TP, interval ="prediction")
```

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

